% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.
% توجه داشته باشید که جدول حاوی مشخصات پایان‌نامه/رساله، به طور خودکار، رسم می‌شود.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\baselineskip=0.6cm
\begin{latin}
\latinuniversity{Shahid Beheshti University}
\latinfaculty{Faculty of Mathematical Sciences}
\latindegree{Master}
%group:
\latinsubject{Department of Data \& Computer Science}
\latinfield{Computer Sciences - Data Mining}
\latintitle{self-supervised learning on spiking neural network}
\firstlatinsupervisor{Dr.Hadi Farahani}
\secondlatinsupervisor{Dr. Saeed Reza Kheradpisheh}
%\firstlatinadvisor{Dr. ZZZ}
%\secondlatinadvisor{Second Advisor}
\latinname{Yeganeh}
\latinsurname{Bahari Asl}
\latinthesisdate{September 2023}
\latinkeywords{Spiking neural networks, self-supervised learning, data classification}
\en-abstract{\noindent 
In this thesis, we examine and introduce spiking neural networks as a new generation of neural networks. Inspired by the structure of the brain, these networks encode and process information through precisely timed spike trains. Unlike the rest of the neural networks, in this type of network, the neurons are resting except when generating spikes, and this property makes the structure of these networks optimal and uses less memory.
In this research, we investigate self-supervised learning methods in spiking neural networks. This method has the ability to use techniques such as data augmentation to perform learning in a redundant network of labeled data.
Finally, the aim of this research is to build an optimal spiking neural network with the capability of self-supervised learning methods to generate representations from the MNIST and CIFAR10 datasets without the need for data labels, and to use these representations for various tasks such as supervised classification. This research tries to finally create more accuracy on the classification methods on the data set by making these representations.
}
\latinvtitle
\end{latin}